%%%
\acknowledgments

I would like to thank my supervisor Prof.Prabhu Ramachandran for giving me an
opportunity to pursue the PhD program under him. I am very thankful for all his
support through out my stay at IIT Bombay and the freedom to pursue my interests
in different fields.

I would like to thank Prof. Chandra Shekar for his help. I
would like to thank my colleague Abhinav Muta for his help and excellent
discussions through out my stay at IIT Bombay. I want to thank Pawan Negi for
his in valuable technical discussions.

I thank Vinay Narasimhan for his support in providing me all the resources to
run my simulations on time.


% I thank staff at IIT Bombkay all who contributed
% direct or indirect way in helping me to complete my PhD.

I would like to thank all my friends, family.


I would like to thank a few living and non-living mentors with out whom this PhD
wouldn't be possible. Firstly, Nietzsche, Ayn Rand, Schopenhaeur for their great
insights into living a great life
% , and I am deeply indebted for their knowledge
% and thankful for their thoughts and writings for making my life easier and to
% achieve greater power.
In living mentors, I thank Novak Djokovic, Lewis Hamilton
from which I took constant inspiration through out my PhD.
% Thankful for Tennis for giving the mental strength of steel.

I would like to thank my dance friends, Ananya Aishwarya and Singham Naresh for
all the good time.


\signature{\today}
%\signature[Indian Institute of Technology Bombay]{\today}

%========================================================================

%%% Local Variables:
%%% mode: latex
%%% TeX-master: "../mainrep"
%%% End:
