%%%
\listofpublications

\subsection*{Journal proceedings}

\begin{itemize}
\item \textbf{Dinesh Adepu} and Prabhu Ramachandran. ``\textbf{A corrected transport-velocity
  formulation for fluid and structural mechanics with SPH}''. in : arXiv preprint
  arXiv:2106.00756 (2021). Under review.
\item \textbf{Dinesh Adepu} and Prabhu Ramachandran. ``\textbf{Improved collision handling of
  elastic solids in SPH using a contact force model}''. in : Engineering Archive
  preprint (Aug. 2022). Under review.
\item Prabhu Ramachandran, Aditya Bhosale, Kunal Puri, Pawan Negi, Abhinav Muta,
  \textbf{Adepu Dinesh}, Dileep Menon, Rahul Govind, Suraj Sanka, Amal S. Sebastian,
  Ananyo Sen, Rohan Kaushik, Anshuman Kumar, Vikas Kurapati, Mrinalgouda Patil,
  Deep Tavker, Pankaj Pandey, Chandrashekhar Kaushik, Arkopal Dutt, and Arpit
  Agarwal. 2021. ``\textbf{PySPH : A Python-based Framework for Smoothed Particle
  Hydrodynamics}''. ACM Trans. Math. Softw. 47, 4, Article 34 (December 2021), 38
  pages.
\end{itemize}


\subsection*{Conference proceedings}
\label{sec:conf-proc}
\begin{itemize}
\item Dinesh Adepu and Prabhu Ramachandran. "Fluid-Structure Interaction with an
  Updated Lagrangian Smoothed Particle Hy- drodynamics". in : 9th International
  and 49th National Conference of Fluid Mechanics and Fluid Power (FMFP-2022)
  (Dec. 2022)
\end{itemize}




%%======================================================================
%%% Local Variables:
%%% mode: latex
%%% TeX-master: "../mainrep"
%%% End:
